Analysis of NLA17 Dissolved Gas Indicator

### 2020-10-15 scripts/dgIndicatorAnalysis.Rmd
I specified getting the latest dataframe.  Cleaned names and filtered out AK sites.  Specified projection for geopackage.

```{r}
# Read data file
load(paste0(localPath, 
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2020-02-25.RData"))

@@

```{r}
# These are the main response variables.
dg %>% 
  select(dissolved.co2, dissolved.ch4, dissolved.n2o, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio) %>%
  {summary(.)}
```

@@

dg_1 <- select(dg,site.id:map.lon.dd, dissolved.co2, dissolved.ch4, dissolved.n2o, WSA9, WSA9_NAME)
names(dg_1)
dg_1 <- clean_names(dg_1) # underscores are "safer" names used in GIS
names(dg_1)
# To enable spatial analysis of the data, the dataframe will be converted to a 'simple features' (sf) object.
# Define coordinates
coords <- data.frame(longitude = dg_1$map_lon_dd, latitude = dg_1$map_lat_dd)

dg_sf1 <- st_as_sf(dg_1, coords = c("map_lon_dd", "map_lat_dd"), 
                  crs = 4269) %>% # standard for lat/lon
  st_transform(4326) # 4326 is just the EPSG identifier of WGS84. WGS84 comprises a standard coordinate frame for the Earth, a datum/reference ellipsoid for raw altitude data, and a gravitational equipotential surface (the geoid) that defines the nominal sea level.
st_crs(dg_sf1)

dg_sf1 <- filter(dg_sf1, sample_source == "DG") # now 1185 obs.
st_crs(dg_sf1)

@@

# Check CRS
st_crs(ecoR)
names(ecoR)

ecoR1 <- st_transform(ecoR, 4326) %>% 
  select(OBJECTID, WSA9, WSA9_NAME) # Grab variables of interest
st_crs(ecoR1)

# write out dg.sf and ecoR as two layers in geopackage, gpkg, geodatabase
# 74. Creating a geopackage geodatabase, then adding more layers
# https://github.com/r-spatial/sf/issues/392
st_write(dg_sf1, dsn = file.path(getwd(), "nladg_v1.gpkg"), layer = "dg_sf1", driver = "GPKG", quiet = FALSE)
st_layers("nladg_v1.gpkg")

# https://gis.stackexchange.com/questions/223240/writing-multiple-layers-to-geopackage-using-writeogr-in-r
st_write(ecoR1, dsn = file.path(getwd(), "nladg_v1.gpkg"), layer = "ecoR1", driver = "GPKG", update = TRUE, quiet = FALSE)
st_layers("nladg_v1.gpkg")

>>>>

```{r}
# Read data file commented out b/c dataMunge.Rmd creates dg assignment based on latest text file nla17gasDataAggregated_2020-10-08.txt
 # load(paste0(localPath, 
 #            "/Environmental Protection Agency (EPA)/",
 #            "ORD NLA17 Dissolved Gas - Documents/",
 #            "inputData/dg.2020-10-09.RData"))

@@

```{r}
# These are the main response variables.
dg %>% 
  select(dissolved.co2, dissolved.ch4, dissolved.n2o, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio) %>%
  {summary(.)}

dg %>% filter(WSA9 != "AK") %>%
  select(dissolved.co2, dissolved.ch4, dissolved.n2o, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio) %>%
  {summary(.)}

dg %>% filter(WSA9 != "AK") %>% 
  ggplot(aes(as.factor(x = WSA9), y = log(dissolved.n2o))) + geom_boxplot()

dg %>% filter(WSA9 != "AK") %>% 
  ggplot(aes(as.factor(x = WSA9), y = (n2o.sat.ratio))) + geom_boxplot()
```

@@

dg_1 <- select(dg,site.id:map.lon.dd, dissolved.co2, dissolved.ch4, dissolved.n2o, WSA9, WSA9_NAME)
names(dg_1)
dg_1 <- clean_names(dg_1) %>% filter(wsa9 != "AK") # underscores are "safer" names used in GIS
names(dg_1)
# To enable spatial analysis of the data, the dataframe will be converted to a 'simple features' (sf) object.
# Define coordinates
coords <- data.frame(longitude = dg_1$map_lon_dd, latitude = dg_1$map_lat_dd)

dg_sf1 <- st_as_sf(dg_1, coords = c("map_lon_dd", "map_lat_dd"), 
                  crs = 4269) %>% # standard for lat/lon
  st_transform(5070) # 4326 is just the EPSG identifier of WGS84. WGS84 comprises a standard coordinate frame for the Earth, a datum/reference ellipsoid for raw altitude data, and a gravitational equipotential surface (the geoid) that defines the nominal sea level.  5070 is for Albers equal Area.
st_crs(dg_sf1)

dg_sf1 <- filter(dg_sf1, sample_source == "DG") # now 1219 obs vs. previously 1185 obs., why change in sample size
st_crs(dg_sf1)

@@

# Check CRS
st_crs(ecoR)
names(ecoR)
# changed from 4326 to 5070
ecoR1 <- st_transform(ecoR, 5070) %>% 
  select(OBJECTID, WSA9, WSA9_NAME) # Grab variables of interest
st_crs(ecoR1)

# write out dg.sf and ecoR as two layers in geopackage, gpkg, geodatabase
# 74. Creating a geopackage geodatabase, then adding more layers
# https://github.com/r-spatial/sf/issues/392
# creating a _v1.gpkg having large sample size and should be in Albers
st_write(dg_sf1, dsn = file.path(getwd(), "nladg_v1.gpkg"), layer = "dg_sf1", driver = "GPKG", quiet = FALSE)
st_layers("nladg_v1.gpkg")

# https://gis.stackexchange.com/questions/223240/writing-multiple-layers-to-geopackage-using-writeogr-in-r
st_write(ecoR1, dsn = file.path(getwd(), "nladg_v1.gpkg"), layer = "ecoR1", driver = "GPKG", append = TRUE, quiet = FALSE)
st_layers("nladg_v1.gpkg")
#CPL polygon not appearing in geopackage
